Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-02 paper/paper.tex
conclusion

\subsection{Comparison with other priors}
\begin{figure}
\centering
  \includegraphics[width=\textwidth]{comparePrior.png}
\caption{Comparison with common prior: A visualization of the posterior pdf for a subsection of TGAS stars, shown as the expectation value and the sqrt of the variance as the uncertainty. On the left is the posterior pdf using our \cmd\ prior, and on the right is the posterior pdf when using the exponentially declining spatial density, a common prior used when inferring parallaxes. The scale of the exponentially declining spatial density prior is XXX, the optimal value found in YYY. Using the \cmd\ as a prior generates a posterior pdf that has smaller variance.}
\label{fig:comparePrior}
\end{figure}

@@

\section{Conclusion}
Data driven prior of \cmd\ in parallax inference is a good idea

>>>>

\subsection{Comparison with other priors}
\begin{figure}
\centering
  \includegraphics[width=\textwidth]{comparePrior.png}
\caption{Comparison with common prior: A visualization of the posterior pdf for a subsection of TGAS stars, shown as the expectation value and the sqrt of the variance as the uncertainty. On the left is the posterior pdf using our \cmd\ prior, and on the right is the posterior pdf when using the exponentially declining spatial density, a common prior used when inferring parallaxes. The scale of the exponentially declining spatial density prior is 1.35 kpc, the optimal value found in \cite{astraatmadja16a}. Using the \cmd\ as a prior generates a posterior pdf that has smaller variance.}
\label{fig:comparePrior}
\end{figure}

@@

\section{Conclusion}
If you want a conclusion, re-read the abstract
